### 2019-07-17 manuscript/methods.tex
small edits in Methods

In order to test our hypotheses about lineage diversification and trait macroevolution, we fitted 29 state-dependent speciation and extinction models (SSE) to previous work on diversification \citep[BiSSE, MuSSE, HiSSE;][]{maddison_2007, fitzjohn_2012, beaulieu_2016}.
SSE models parameters that describe per-lineage rates of speciation and extinction, specific to each character state (denoted $\lambda$ and $\mu$, respectively, with subscripts to indicate the state), along with rates of transitions between states (denoted $\rho$ for polyploidization, $\delta$ for diploidization, and $q_{IC}$ for loss of self-incompatibility).
The full set of models and all their rate parameters are detailed in \cref{fig:allmodels}.
Here, we summarize how each model allows us to assess whether diversification is best explained by variation in ploidy, breeding system, their combination, or some unknown factor.

@@

In order to investigate the association between ploidy level and diversification, we first employed a model  (M1), previously used by \citet{mayrose_2011}, with each taxon classified as diploid $(D)$ or polyploid $(P)$.
Although this model can be powerful in studies of trait evolution, it is prone to incorrectly reporting that a trait is associated with diversification differences \citep{maddison_2015, rabosky_2015}.
We therefore define several models that incorporate additional forms of diversification rate heterogeneity.

@@

We additionally fit three models in which both ploidy and a hidden states could influence diversification (M3--M5).
These models differ in whether transitions between the hidden states are symmetric or asymmetric, and whether the polyploidization rate depends on the hidden state.
Comparing M1--M5 allows us to test whether ploidy is associated with diversification differences on top of the differences potentially explained by an unknown factor (\cref{table:bayesfactors}).

@@

We propose five breeding system models following the same logic as the first ploidy models.
Under the simplest breeding system and diversification model (M11), species are classified as self-incompatible $(I)$ or self-compatible $(C)$.
This is the same model as in the analysis presented in \citet{goldberg_2010} but with an updated phylogeny \citep{sarkinen_2013} and a larger aggregated dataset.

@@

Self-incompatibility is homologous in all Solanaceae species in which S-alleles have been cloned and controlled crosses performed.
All species sampled to date possess a non-self recognition, RNase-based gametophytic self-incompatibility \citep[shared even with other euasterid families;][]{ramanauskas_2017}.
Furthermore, species that are distantly related within this family carry closely-related alleles, with deep trans-specific polymorphism at the locus that controls the SI response \citep{ioerger_1990, igic_2006}.
The breeding system in Solanaceae has strong evidence that the $I$ state is ancestral in the family, and that the SI mechanism was not regained.
Therefore, for all breeding system models, we estimated a transition rate from $I$ to $C$  but not the reverse ($q_{CI}=0$).
% This is an important assumption because ancestral state reconstruction in the models might differ when polyploidy and breeding system are analyzed as independent in the Solanaceae tree.
%
%B: What happens if SC->SI is not fixed? Asking for a friend.  E: Surprisingly, Rosana reports, results are not turned on their head. 
%B: Whew, I was worried. Er, "friend" says thanks. R- Your welcome, by mistake I did that model with reversibility from C to I. I didn't run it for as long as the rest but preliminary ancestral reconstructions seem almost identical when you add that parameter than when you don't.

@@

The simplest model classifies each species as either SI diploid $(ID)$, SC diploid $(CD)$, or SC polyploid $(CP)$; recall that SI polyploids do not occur (M16).
Each of these states may again be associated with different rates of speciation and extinction, and the allowable transitions are loss of SI within the diploid state (from $ID$ to $CD$), loss of SI via polyploidization (from $ID$ to $CP$), and polyploidization while SC (from $CD$ to $CP$).
% The total rate of loss of self-incompatibility, \ie transitions out of $ID$, is $q_{IC} + \rho_I$.
% E: Can we call it something other than q_IC?  It's a bit confusing to have the same parameter mean different things in different models.

As for the previous models of only one trait, we then allow diversification to be influenced by only a hidden trait (M17), or by both ploidy, breeding system, as well as a hidden trait (M18--M20) with varying degrees of complexity in the hidden trait transitions (\cref{supptable:M16M20}).
We add this hidden trait layer on top of our three-state model \citep[similar to][]{caetano_2018, huang_2018}.
We also fit the analogous models but allowing for diploidization (M21--M25, \cref{supptable:M21M25}).

@@

The models described so far allow us to assess the contributions of our two focal characters---ploidy and breeding system---to lineage diversification, but they do not reveal whether it is valuable to include both characters in the analysis.
Assessing whether diversification heterogeneity is better explained by simultaneous consideration of both characters, rather than either one alone, requires the calculation of the likelihood function of the data given a specific model.
However, the likelihood of the data given a model differs---in our case, two-state versus three-state models---because the proposed models use different state spaces: $D/P$ versus $I/C$ versus $IC/CD/CP$. Therefore, the use of different data results in incomparable models.

In order to compare fits of ploidy-only vs. breeding system-only vs. combined trait models, we extend a  technique proposed in the work by \citet{tarasov_2019} for state `lumping.'
We use the state space of the $IC/CD/CP$ model but constrain the rate parameters to mimic the behavior of the single-trait models.
First we lump together $ID$ and $CD$ to form the diploid state, mimicking the $D/P$ model (M26).
Then we lump together $CD$ and $CP$ to form the self-compatible state, mimicking the $I/C$ model (M28).
We further add a hidden character to each of these models (M27 and M29), and the compare this group of models in table \cref{table:lumped}

We do not include additional models with diploidization because this reverse ploidy transition renders the models non-lumpable \citep{tarasov_2019}.
To lump two states, it is a necessary and sufficient condition that the transition rates from the lumped state to the singular state are equal  \citet{tarasov_2019}.
When lumping compatible state $CD$ and $CP$ the the rate at which they back to state $ID$ is zero for both, thus, compatible states are lumpable. 
Then, we define a single $q_0$ parameter as the new rate from incompatible to compatible going into the lumped state $(CD,CP)$.
By doing so, we can define the lumped model M28 (\cref{figure:lumped}E) that is equivalent to M1 but comparable to M16.
We repeat this process to create the lumped model M26for $D/P$ by restricting the polyploidy rate to be $rho_0$ out of the lumped state $(ID,CD)$
For the diploidization models, $CP$ goes back to $CD$ with rate $\delta$ but the rate from $CP$ back to $ID$ is 0.
Since $\delta \neq 0$, the models with diplodization cannot be lumped to be compared to the tree-state models.
% E: further explanation needed? R- I added a simple math explanation. Let me know if it is okay

@@

Considering ploidy and breeding system together, there are two evolutionary pathways from SI diploid to SC polyploid \citep{brunet2001, robertson_2011}.
In the one-step pathway, the $CP$ state is produced directly from the $ID$ state when whole genome duplication disables SI.
In the two-step pathway, the $CD$ state is an intermediate: SI is first lost, and later the SC diploid undergoes polyploidization.
We quantify the relative contribution of these pathways to polyploidy in two ways, each using the maximum \textit{a posteriori} (MAP) estimates of rates from the simplest model that includes both traits (M16).

@@

Second, we consider not only transitions between states but also diversification within each state.
State-dependent diversification can change the relative contributions of the two pathways.
For example, if the net diversification rate is small for $CD$, the two-step pathway will contribute relatively less.
We therefore include the difference between speciation and extinction along the diagonal elements of the propagation matrix.
As before, matrix exponentiation provides the relative chance of changing from one state to any other state after time $t$.
In this case, however, these are not probabilities because diversification changes the number of lineages as time passes. %B: FIXME, we'll hear complaints again about "this," "these," and ... "their." (below)
We can still use their ratios to consider the relative contribution of each pathway, analogous to the normalized age structure in a growing population. % R- here a reference would be nice  E: Does Jake have a favorite ref? Otherwise, I guess a basic ecology textbook.
%
% E & R todo ?: for the case with net div, write out the propagation matrix and equations for pathway contributions
%
% E: I don't think we need this section now that diploidization is in each of the sections above.  But I'm saving this text in case we want to put some of it in Results.
%--------------------------------------------------
% \subsubsection{Diploidization as an exploratory hypothesis}
%
% The models described above allow polyploidization but not its reverse.
% We explored the effects of allowing diploidization by adding a parameter $\delta$ for transitions from $P$ back to $D$ (in the $D/P$ and $D/P+A/B$ models) or from $CP$ back to $CD$ (in the $I/C$ and $I/C+A/B$ models); we did not allow transitions from $CP$ back to $ID$ because that would include regain of SI.
% Previous modeling approaches \citep{mayrose_2011} have argued against inferring diploidization rates when using ploidy data that comes from classifications based on chromosome number multiplicity or chromosome number change models like chromEvol \citep{mayrose_2010, glick2014, mayrose_2015, freyman_2017}, which assume only aneuploid change and polyploidization.
% Our ploidy classifications, however, when possible also incorporated information on chromosome multiplicity at the genus level and author conclusions within original studies with alternative sources of information (\eg geographic distribution, genus ploidy distribution).
% Since it is not known whether diploidization can be detected under these additional ploidy classifications, we fit models with and without diploidization in order to test whether the conclusions about diversification are sensitive to including diploidization.
% In our models, the diploidization parameter (or its absence, $\delta=0$), represents an opportunity to explore a possibly significant assumption that may not decisively affect interactions among ploidy, breeding system, and diversification.
%--------------------------------------------------

@@

Parameters for each of the 29 models were estimated using RevBayes \citep{hoehna_2016}.
Scripts for analyses and key results are available as Supplementary Information. % FIXME more permanent than \url{https://github.com/roszenil/solploidy}.
We accounted for incomplete sampling in all analyses by setting the probability of sampling a species at the present to $651/3000$ \citep[using the method of][]{fitzjohn_2009} since the Solanaceae family has approximately 3,000 species \citep{solsource}.
For all models, we assumed that speciation and extinction parameters had log-normal prior distributions with means equal to the expected net diversification rate $(\text{number of taxa} / [2 \times \text{root age}])$ and standard deviation $0.5$.
Priors for parameters defining trait changes were assumed to be gamma distributed with parameters $k=0.5$ and $\theta=1$. 
For each model, a Markov chain Monte Carlo \citep[MCMC;][]{metropolis1953equation,Hastings1970} was run in the high-performance computational cluster at the Minnesota Supercomputing Institute, which allowed for 5,000 generations of burn-in and a minimum of 200,000 generations of MCMC for each of the  models. % FIXME see referee comment about reporting convergence, not runtime
Convergence and mixing of each MCMC chain was determined by ensuring the effective sample size of each parameter was over 200.

We report posterior distributions for the model parameters in \cref{figure:netdivall}, and also for the compound parameters of net diversification ($\lambda - \mu$) and extinction fraction ($\mu / \lambda$) for each state.
Additionally, ancestral states at each node in the phylogeny were sampled jointly during the MCMC analyses every 100 generations.
Ancestral state estimations for all models show the maximum \emph{a posteriori} estimates of the marginal probability distributions for each of the 650 internal nodes for each of the models in \cref{figure:netdivall}. (\cref{suppfigure:DPnodipasr,suppfigure:DPnodipABasr,suppfigure:ICasr,suppfigure:ICABasr,suppfigure:IDCDCPnodipasr,suppfigure:IDCDCPnodipABasr}). % FIXME: I'm confused about if these are joint or marginal?  A bit more explanation would help. R: Marginal explanation added

@@

We calculated the marginal log-likelihood for each of the models using fifty stepping stone steps under the methodology of \citet{xie_2010}, implemented in RevBayes \citep{hoehna_2016}.
Each stepping stone step was found by calculating at least 500 generations of burn-in followed by a total of 1,000 MCMC steps (\cref{table:marginallike}).

Using the marginal likelihood values, we calculated Bayes factors to argue five key biological and methodological questions:
\begin{enumerate}
\item Are diversification patterns only determined by hidden states and not the traits of interest?---Comparison of character independent models against hidden state (\cref{table:bayesfactors,table:M11M15,supptable:M6M10,supptable:M16M20,supptable:M21M25}).
\item Are hidden states necessary to explain diversification rate heterogeneity?---Comparison of simple models against hidden state models (\cref{supptable:testaddhidden}).
\item Does a second focal trait add information about the diversification process?---Comparison of lumped models against IC/CD/CP models (\cref{figure:lumped,table:lumped}).
\item Are conclusions robust to assumptions about hidden state transitions?---Comparison amongst hidden states models with equal hidden rates and asymmetrical rates (\cref{suppfigure:asymmetric,supptable:asymmetry}).
\item Is there evidence for diploidization?---Comparison amongst models with and without diploidization (\cref{suppfigure:alldip,supptable:testdiploidization}).
\end{enumerate}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states.pdf} % FIXME: update numbers
\caption{
Character states used for each of the models.
Each species retained on the tree belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known. Character state abbreviations: $I$ for self-incompatible, $C$ for self-compatible, $D$ for diploid, $P$ for polyploid, $?$ for unknown.
(A) The five categories and the number of species in our data for each category.
Because polyploidization breaks this form of self-incompatibility, self-incompatible species with unobserved ploidy ($I?$) are taken to be diploid ($ID$), and polyploid species with unobserved breeding system ($?P$) are taken to be SC.
(B) Category groupings into states for each model type.
For example, there are 70 species that are SC with unknown ploidy. % Fixed
In the $D/P$ models these are coded as either $D$ or $P$ (uncertain/consistent with either state), in the $I/C$ models they are coded as $C$, and in the $ID/CD/CP$ models they are coded as either $CD$ or $CP$.
In the hidden state models, all species were coded as consistent with both $A$ and $B$. Two species \textit{Lycium californicum} and \textit{Solanum bulbocastanum} are simultaneously ID and CP and by adding them the sample adds to the total of 651 taxa used for analyses.
}
\label{figure:stateclassifications}
\end{figure}

>>>>

In order to test our hypotheses about lineage diversification and trait macroevolution, we fit 29 state-dependent speciation and extinction models \citep[BiSSE, MuSSE, HiSSE;][]{maddison_2007, fitzjohn_2012, beaulieu_2016}.
SSE models contain parameters that describe per-lineage rates of speciation and extinction, specific to each character state (denoted $\lambda$ and $\mu$, respectively, with subscripts to indicate the state), along with rates of transitions between states (denoted $\rho$ for polyploidization, $\delta$ for diploidization, and $q_{IC}$ for loss of self-incompatibility).
The full set of models and all their rate parameters are detailed in \cref{fig:allmodels}.
Here, we summarize how each model allows us to assess whether diversification is best explained by variation in ploidy, breeding system, their combination, or some unknown factor.

@@

In order to investigate the association between ploidy level and diversification, we first employed a model (labeled M1), previously used by \citet{mayrose_2011}, with each species classified as diploid $(D)$ or polyploid $(P)$.
Although this model can be powerful in studies of trait evolution, it is prone to incorrectly reporting that a trait is associated with diversification differences \citep{maddison_2015, rabosky_2015}.
We therefore define several models that incorporate additional forms of diversification rate heterogeneity.

@@

We additionally fit three models in which both ploidy and a hidden trait could influence diversification (M3--M5).
These models differ in whether transitions between the hidden states are symmetric or asymmetric, and whether the polyploidization rate depends on the hidden state.
Comparing M1--M5 allows us to test whether ploidy is associated with diversification differences on top of the differences potentially explained by an unknown factor (\cref{table:bayesfactors}).

@@

We propose five breeding system models following the same logic as the ploidy models above.
Under the simplest breeding system and diversification model (M11), species are classified as self-incompatible $(I)$ or self-compatible $(C)$.
This is the same model as in the analysis presented in \citet{goldberg_2010} but with an updated phylogeny \citep{sarkinen_2013} and a larger aggregated dataset.

@@

Self-incompatibility is homologous in all Solanaceae species in which S-alleles have been cloned and controlled crosses performed.
All species sampled to date possess a non-self recognition, RNase-based gametophytic self-incompatibility \citep[shared even with other euasterid families;][]{ramanauskas_2017}.
Furthermore, species that are distantly related within this family carry closely-related alleles, with deep trans-specific polymorphism at the locus that controls the SI response \citep{ioerger_1990, igic_2006}.
Thus, there is strong evidence in Solanaceae that the $I$ state is ancestral in the family, and that the SI mechanism was not regained.
Therefore, for all breeding system models, we estimated a transition rate from $I$ to $C$  but not the reverse ($q_{CI}=0$).
% This is an important assumption because ancestral state reconstruction in the models might differ when polyploidy and breeding system are analyzed as independent in the Solanaceae tree.
%
%B: What happens if SC->SI is not fixed? Asking for a friend.  E: Surprisingly, Rosana reports, results are not turned on their head. 
%B: Whew, I was worried. Er, "friend" says thanks. R- Your welcome, by mistake I did that model with reversibility from C to I. I didn't run it for as long as the rest but preliminary ancestral reconstructions seem almost identical when you add that parameter than when you don't.

@@

The simplest model (M16) classifies each species as either SI diploid $(ID)$, SC diploid $(CD)$, or SC polyploid $(CP)$; recall that SI polyploids do not occur.
Each of these states may again be associated with different rates of speciation and extinction, and the allowable transitions are loss of SI within the diploid state (from $ID$ to $CD$), loss of SI via polyploidization (from $ID$ to $CP$), and polyploidization while SC (from $CD$ to $CP$).
% The total rate of loss of self-incompatibility, \ie transitions out of $ID$, is $q_{IC} + \rho_I$.
% E: Can we call it something other than q_IC?  It's a bit confusing to have the same parameter mean different things in different models.

As for the previous models of only one trait, we then allow diversification to be influenced by only a hidden trait (M17), or by ploidy, breeding system, and a hidden trait (M18--M20) with varying degrees of complexity in the hidden trait transitions (\cref{supptable:M16M20}).
We add this hidden trait layer on top of our three-state model \citep[similar to][]{caetano_2018, huang_2018}.
We also fit the analogous models but allowing for diploidization (M21--M25, \cref{supptable:M21M25}).

@@

The models described so far allow us to assess the contributions of our two focal characters---ploidy and breeding system---to lineage diversification, but they do not reveal whether it is valuable to include both characters in the analysis.
To answer this question with statistical model comparisons requires comparing the likelihood of the data given each model.
This is impossible for the ploidy and breeding system models presented so far, however, because the data are different for the different models: they use either the $D/P$ or the $I/C$ or the $IC/CD/CP$ state spaces.
Therefore, the use of different data results in incomparable models.

In order to compare fits of ploidy-only \vs breeding system-only \vs combined trait models, we use the technique of `lumping' states together \citep{tarasov_2019}.
We use the state space of the $IC/CD/CP$ model but constrain the rate parameters to mimic the behavior of the single-trait models.
First we lump together $ID$ and $CD$ to form the diploid state, mimicking the $D/P$ model (M26).
Then we lump together $CD$ and $CP$ to form the self-compatible state, mimicking the $I/C$ model (M28).
We further add a hidden character to each of these models (M27 and M29), and then compare this group of models (\cref{table:lumped}).

We do not include additional models with diploidization because this reverse ploidy transition renders the models non-lumpable.
To lump states requires that the transition rates from the lumped state to the singular state be equal \citep{tarasov_2019}.
When including diploidization, transitions from $CP$ to $CD$ are at rate $\delta$ but transitions from $CP$ to $ID$ do not occur.
Because $ID$ and $CD$ would be lumped to mimic the $D/P$ model, this model is non-lumpable when $\delta \ne 0$.
When lumping $CD$ and $CP$, however, the transition rate to $ID$ is zero for both, so the SC states are lumpable. 
Thus, we can compare models to test whether it is advantageous to include both traits, but only when ignoring diploidization.
% E: Below was all good, but it seemed like more detail than necessary.
% Then we define a single parameter $q_0$ going into the lumped state $(CD,CP)$ as the new rate from SI to SC.
% This defines the lumped model M28 (\cref{figure:lumped}E) that is equivalent to M1 but comparable to M16.
% We repeat this process to create the lumped model M26 for $D/P$ by restricting the polyploidy rate to be $rho_0$ out of the lumped state $(ID,CD)$.
% When including diploidization, however, transitions from $CP$ to $CD$ are at rate $\delta$ but transitions from $CP$ to $ID$ do not occur.
% Since $\delta \neq 0$, the models with diplodization cannot be lumped to be compared to the three-state models.

@@

Considering ploidy and breeding system together, there are two evolutionary pathways from SI diploid to SC polyploid \citep{brunet2001, robertson_2011}.
In the one-step pathway, the $CP$ state is produced directly from the $ID$ state when whole genome duplication disables SI.
In the two-step pathway, the $CD$ state is an intermediate: SI is first lost, and later the SC diploid undergoes polyploidization.
We quantify the relative contribution of these pathways to polyploidy in two ways, each using the median estimates of rates from the simplest model that includes both traits (M16).

@@

Second, we consider not only transitions between states but also diversification within each state.
State-dependent diversification can change the relative contributions of the two pathways.
For example, if the net diversification rate is small for $CD$, the two-step pathway will contribute relatively less.
We therefore include the difference between speciation and extinction along the diagonal elements of the propagation matrix.
As before, matrix exponentiation provides the relative chance of changing from one state to any other state after time $t$.
In this case, however, these are not probabilities because diversification changes the number of lineages as time passes. %B: FIXME, we'll hear complaints again about "this," "these," and ... "their." (below)
We can still use ratios, however, to consider the relative contribution of each pathway, analogous to the normalized age structure in a growing population. % R- here a reference would be nice  E: Does Jake have a favorite ref? Otherwise, I guess a basic ecology textbook.
%
% E & R todo ?: for the case with net div, write out the propagation matrix and equations for pathway contributions
%
% E: I don't think we need this section now that diploidization is in each of the sections above.  But I'm saving this text in case we want to put some of it in Results.
%--------------------------------------------------
% \subsubsection{Diploidization as an exploratory hypothesis}
%
% The models described above allow polyploidization but not its reverse.
% We explored the effects of allowing diploidization by adding a parameter $\delta$ for transitions from $P$ back to $D$ (in the $D/P$ and $D/P+A/B$ models) or from $CP$ back to $CD$ (in the $I/C$ and $I/C+A/B$ models); we did not allow transitions from $CP$ back to $ID$ because that would include regain of SI.
% Previous modeling approaches \citep{mayrose_2011} have argued against inferring diploidization rates when using ploidy data that comes from classifications based on chromosome number multiplicity or chromosome number change models like chromEvol \citep{mayrose_2010, glick2014, mayrose_2015, freyman_2017}, which assume only aneuploid change and polyploidization.
% Our ploidy classifications, however, when possible also incorporated information on chromosome multiplicity at the genus level and author conclusions within original studies with alternative sources of information (\eg geographic distribution, genus ploidy distribution).
% Since it is not known whether diploidization can be detected under these additional ploidy classifications, we fit models with and without diploidization in order to test whether the conclusions about diversification are sensitive to including diploidization.
% In our models, the diploidization parameter (or its absence, $\delta=0$), represents an opportunity to explore a possibly significant assumption that may not decisively affect interactions among ploidy, breeding system, and diversification.
%--------------------------------------------------

@@

Parameters for each of the 29 models were estimated using RevBayes \citep{hoehna_2016}.
Scripts for analyses and key results are available as Supplementary Information. % FIXME more permanent than \url{https://github.com/roszenil/solploidy}.
We accounted for incomplete sampling in all analyses by setting the probability of sampling a species at the present to $651/3000$ \citep[using the method of][]{fitzjohn_2009} since the Solanaceae family has approximately 3,000 species \citep{solsource}.
For all models, we assumed that speciation and extinction parameters had log-normal prior distributions with means equal to the expected net diversification rate $(\text{number of taxa} / [2 \times \text{root age}])$ and standard deviation $0.5$.
Priors for parameters defining trait changes were assumed to be gamma distributed with parameters $k=0.5$ and $\theta=1$. 
For each model, a Markov chain Monte Carlo \citep[MCMC;][]{metropolis1953equation,Hastings1970} was run in the high-performance computational cluster at the Minnesota Supercomputing Institute, which allowed for 5,000 generations of burn-in and a minimum of 200,000 generations of MCMC for each of the models.
Convergence and mixing of each MCMC chain was determined by ensuring the effective sample size of each parameter was over 200.

We report posterior distributions for the model parameters in \cref{figure:netdivall}, and also for the compound parameters of net diversification ($\lambda - \mu$) and extinction fraction ($\mu / \lambda$) for each state.
Additionally, ancestral states at each node in the phylogeny were sampled jointly during the MCMC analyses every 100 generations.
Ancestral state estimations for all models show the maximum \emph{a posteriori} estimates of the marginal probability distributions for each of the 650 internal nodes for each of the models in \cref{figure:netdivall}. (\cref{suppfigure:DPnodipasr,suppfigure:DPnodipABasr,suppfigure:ICasr,suppfigure:ICABasr,suppfigure:IDCDCPnodipasr,suppfigure:IDCDCPnodipABasr}).

@@

We calculated the marginal log-likelihood for each of the models using fifty stepping stone steps under the methodology of \citet{xie_2010}, implemented in RevBayes \citep{hoehna_2016}.
Each stepping stone step was found by calculating at least 500 generations of burn-in followed by a total of 1,000 MCMC steps. % (\cref{table:marginallike}) updated ref?

Using the marginal likelihood values, we calculated Bayes factors to answer five key biological and methodological questions:
\begin{enumerate}
\item Are diversification patterns only determined by hidden states and not the traits of interest?---Comparison of character independent models against hidden state (\cref{table:bayesfactors,table:M11M15,supptable:M6M10,supptable:M16M20,supptable:M21M25}).
\item Are hidden states necessary to explain diversification rate heterogeneity?---Comparison of simple models against hidden state models (\cref{supptable:testaddhidden}).
\item Does a second focal trait add information about the diversification process?---Comparison of lumped models against IC/CD/CP models (\cref{figure:lumped,table:lumped}).
\item Are conclusions robust to assumptions about hidden state transitions?---Comparison amongst hidden states models with equal hidden rates and asymmetrical rates (\cref{suppfigure:asymmetric,supptable:asymmetry}).
\item Is there evidence for diploidization?---Comparison amongst models with and without diploidization (\cref{suppfigure:alldip,supptable:testdiploidization}).
\end{enumerate}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states.pdf}
\caption{
Character states used for each of the models.
Each species retained on the tree belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known. Character state abbreviations: $I$ for self-incompatible, $C$ for self-compatible, $D$ for diploid, $P$ for polyploid, $?$ for unknown.
(A) The five categories and the number of species in our data for each category.
Because polyploidization breaks this form of self-incompatibility, self-incompatible species with unobserved ploidy ($I?$) are taken to be diploid ($ID$), and polyploid species with unobserved breeding system ($?P$) are taken to be SC ($CP$).
(B) Category groupings into states for each model type.
For example, there are 70 species that are SC with unknown ploidy.
In the $D/P$ models these are coded as $D$ and $P$ (uncertain/consistent with either state), in the $I/C$ models they are coded as $C$, and in the $ID/CD/CP$ models they are coded as $CD$ and $CP$.
In the hidden state models, all species were coded as consistent with both $A$ and $B$.
Two species, \emph{Lycium californicum} and \emph{Solanum bulbocastanum}, are simultaneously $ID$ and $CP$, and by adding them the sample adds to the total of 651 taxa used for analyses.
}
\label{figure:stateclassifications}
\end{figure}
